\documentclass[addpoints,12pt]{exam}
\newcommand{\ds}{\displaystyle}
\usepackage[margin=0.8in]{geometry}
\usepackage{subcaption}
\usepackage{tikz}
\usepackage{amssymb,amsmath,graphicx,wrapfig,verbatim,wasysym, enumitem,psfragx,color}
\usepackage{multicol}

%\usepackage{fancyhdr}
%\setlength{\headheight}{13.6pt}
%\pagestyle{fancy}
%\lhead{Math 222}
%\chead{ Midterm 1 }
%\rhead{Spring 2022}

\def\FillInBlank{\rule{3truein} {.01truein}}

% Choose one option (bubbles)
\newcommand{\chooseone}{{\Large$\Circle$\ \ }}


\newcommand{\myleft}{\makebox[.4\textwidth]{First Name:\enspace\hrulefill}}
\newcommand{\myright}{\makebox[.4\textwidth]{Last Name:\enspace\hrulefill}}
\header{\oddeven{\myleft}{}}
    {}

    {\oddeven{\myright}{}}

\footrule

\footer{Math 221}
     {Midterm 2 - Spring 2025}
     {Page \thepage\ of \numpages}

\begin{document}

\begin{questions}

 \question Compute the following definite integrals. Remember that you do not need to simplify
your answer arithmetically.

\begin{parts}




\part[5] $\displaystyle\int_0^{1} t^3(t+1) \, dt$

\vfill




\part[6] $\displaystyle \int_{1}^{4} x^2 + \dfrac{1}{\sqrt{x^3}} +\frac{3}{x^2} \, dx$




\vfill

\end{parts}

\newpage

\question[5] Find the general antiderivative, $F(x),$ of $f(x) = 6x^2 + 2\sin(x) + 3\sec(x)\tan(x) +
4. $

\newpage

\question Consider the curve $6x^3y^2 + 2y -1 = x^2 + y^4 +1 .$

\begin{parts}

\part[7] Compute $\dfrac{dy}{dx}.$
\vfill
\part[3] Find the equation of the tangent line to the curve at the point $(1,-1).$
\vfill

\end{parts}

\newpage

%Find the antiderivative $F$ of the function $f(x) = 4x+ \dfrac{1}{x^3}$ that satisfies the
%condition $F(1) = 3.$

\vfill

\newpage

\question[12] Two cars start moving from the same point. One travels south at 60 miles per
hour, and the other travels west at 25 miles per hour. At what rate is the distance between the
cars increasing 2 hours later?

% ex 4 https://people.tamu.edu/~mvorobet//Math151/F16/s3_10_sol.pdf




\newpage




\question[6] Find all the vertical, horizontal, and slant asymptotes of the following function, if
any. Make sure to check ALL appropriate limits for each type of asymptote.




$$f(x) = \dfrac{5x -4x^3 +6}{x^3+x}$$




\newpage

\question Consider the function $f(x) = x^4- 3x^3+1. $

\begin{parts}

\part[4] For what values of $x$ is the function increasing? Decreasing?
\vfill
\vfill


\part[2] Find the $x$-coordinate(s) of all local maxima or minima of the function. Make sure to
specify for each point if it is a maximum or a minimum.

\vfill




\part[4] In which intervals of $x$ is the function concave up? Concave down?
\vfill
\vfill

\part[2] Find the $x$-coordinate(s) of all inflection points of the function.

\vfill

\end{parts}

\newpage

 \question[12] A landscape architect wishes to enclose a rectangular garden on one side by a
brick wall costing \$30 per foot, and on the other three sides by a metal fence costing \$10 per
foot. If the area of the garden is 1000 square feet, find the dimensions of the garden that
minimizes the cost.

% https://www.youtube.com/watch?v=BOuVKWu6y0Y

\newpage

\question[5] Find a function $f$ such that $f'(t) = 2t+1,$ and $f(-1) = 4.$

\newpage

\question[7] Sketch a graph of a function $f(x)$ that has the following properties:

\begin{itemize}
\item $f(-1)=-5$
\item $\displaystyle\lim_{x\to -\infty} f(x) = 2,$ $\displaystyle\lim_{x\to +\infty}f(x) = 2$
\item $f'(x)>0$ when $-1<x<\infty$

\item $f'(x)<0$ when $-\infty<x<-1$
\item $f''(x)>0$ when $-4<x<2$
\item $f''(x)<0$ when $-\infty<x<-4$ and $2<x<\infty$

\end{itemize}


\begin{center}

\begin{tikzpicture}
\draw[help lines, color=gray!30, dashed] (-7.9,-7.9) grid (7.9,7.9);
\draw[->,ultra thick] (-8,0)--(8,0) node[right]{$x$};
\draw[->,ultra thick] (0,-8)--(0,8) node[above]{$y$};

\end{tikzpicture}
\end{center}

\newpage

\question[7] Find the absolute maximum value and the absolute minimum value of $$f(x) = x^3 –
12x + 23$$ on the interval $[-5, 1].$

\newpage

\question[5] Does there exist a differentiable function $f$ such that $f(2) = 8,$ $ f(4) = 11$ and
$f'(x) \ge 4$ for all $x$? Clearly justify your answer. Answers with no justification will receive no
credit. If you use a theorem, state which theorem
you are using.

\newpage


\question Consider the graph of $y = \sqrt{x}$ above the $x$-axis with $1 \le x\le 9$. In this
problem, you will estimate the area under this curve using 4 rectangles (of equal width) with left
end points.

\begin{parts}
\part[2] Sketch the graph (including the rectangles).
\vspace{2in}

\part[4] Approximate the area. Remember that you don't need to simplify your answer.

\vfill
\vfill

\part[2] Multiple Choice. Fully fill in the circle. The approximation in part (b) is:

\bigskip


 \begin{itemize}[label={}]
\item \chooseone an underestimate of the area under the graph
\item \chooseone an overestimate of the area under the graph
\item \chooseone equal to the area under the graph
\item \chooseone it cannot be determined with the information provided whether the
approximation is an underestimate, an overestimate, or equal to the area under the graph.
\end{itemize}

\bigskip




%\bigskip

 %\part[3] Write down a definite integral that represents the area under the graph of $y =
%\sqrt{x}$ and above the $x$-axis with $1 \le x\le 9. $ You do not need to compute the integral.




\end{parts}

\newpage




%$f(x) = \dfrac{x^3 + 2x^2}{x^2-4}$

%\newpage

%\question Compute the following limits.

%\begin{parts}

%\part[4] $\displaystyle\lim_{x \to \infty} \sqrt{x^2+x} + x$

%\vfill

%\part[4] $\displaystyle\lim_{x \to -\infty} \sqrt{x^2+x} + x$

%\vfill

%\end{parts}


\newpage




%\newpage

%\question[10] Clearly mark the correct answer for each of the following by completely filling in
%the appropriate bubble. \textbf{No justification is needed.}

%\bigskip

%\begin{parts}
%\part If $f'(x) = 2$ everywhere and $f(2) = 4$, then $f(x) = 2x+2$.

% this is false because it fails f(2)=4
%\begin{itemize}[label={}]
%\item \chooseone True
%\item \chooseone False
%\end{itemize}

%\vspace{.4in}


%\end{parts}

\end{questions}

\end{document}
