\documentclass[addpoints,12pt]{exam}
\newcommand{\ds}{\displaystyle}
\usepackage[margin=0.8in]{geometry}
\usepackage{subcaption}
\usepackage{tikz}
\usepackage{amssymb,amsmath,graphicx,wrapfig,verbatim,wasysym, enumitem,psfragx,color}
\usepackage{multicol}

%\usepackage{fancyhdr}
%\setlength{\headheight}{13.6pt}
%\pagestyle{fancy}
%\lhead{Math 222}
%\chead{ Midterm 1 }
%\rhead{Spring 2022}

\def\FillInBlank{\rule{3truein} {.01truein}}

% Choose one option (bubbles)
\newcommand{\chooseone}{{\Large$\Circle$\ \ }}


\newcommand{\myleft}{\makebox[.4\textwidth]{First Name:\enspace\hrulefill}}
\newcommand{\myright}{\makebox[.4\textwidth]{Last Name:\enspace\hrulefill}}
\header{\oddeven{\myleft}{}}
    {}
    {\oddeven{\myright}{}}

\footrule

\footer{Math 221}
     {Midterm 2 - Spring 2024}

    {Page \thepage\ of \numpages}

\begin{document}

\begin{questions}




\question Compute the following definite integrals.

\begin{parts}




\part[7] $\displaystyle\int_0^{\pi/4} \left(\sin(x) + \cos(x) + \sec^2(x) \right)\, dx$

\vfill

\part[7] $\displaystyle\int_1^{2} \left( \dfrac{1}{\sqrt{x}} + 4x^8 + \dfrac{3}{x^2} \, \right)\, dx$

\vfill

%\part[5] $\displaystyle\int_0^{2\pi} \left(\cos(t) + 3\sec^2(t) + 2\sin(t)\right)\, dt$




% \part[6] $\displaystyle\int_{1}^{2} \dfrac{t^3+4t+8}{\sqrt{t}}\, dt$
% \vfill

\part[7] $\displaystyle \int_{1}^4 \frac{t^2 + 8t + \sqrt{t}}{ 2t} \, dt$




\vfill

\end{parts}

\newpage


\vfill




\question[8] Find the antiderivative $F$ of the function $f(x) = 4x+ \dfrac{1}{x^3}$ that satisfies
the condition $F(1) = 3.$

\vfill

\newpage

\question[10] A 13 ft ladder is leaning against a house when its base starts to slide away from
the house. By the time the base of the ladder is 5 ft from the house, the base is moving at a rate
of 2 ft/sec. How fast is the ladder’s top sliding down the wall when the base of the ladder is 5 ft
from the house?

\newpage
\question[10] Find the slope of the tangent line to the curve $(x+y)^8 = 3x^2y^3 +x - 2 $ at the
point $(-1,1).$

\newpage


\question Consider the function $f(x) = \frac{1}{2}x^4- 4x^2+6. $

\begin{parts}

\part[4] For what values of $x$ is the function increasing? Decreasing?
\vfill

\vfill


\part[3] Find the $x$-coordinate of any local maxima or minima of the function. Make sure to
specify for each point if it is a maximum or a minimum.

\vfill

\part[4] For what values of $x$ is the function concave up? Concave down?
\vfill
\vfill

\end{parts}

\newpage




\question Find all the vertical, horizontal, and slant asymptotes of the following functions, if any.

\begin{parts}

\part[6] $f(x) = \dfrac{-2x^2+5x+1}{x-2}$

\vfill

\part[6] $g(x) = \dfrac{x^2 +x -2}{x^2 -1}$




\vfill

\end{parts}




%$f(x) = \dfrac{x^3 + 2x^2}{x^2-4}$




%\newpage

%\question Compute the following limits.

%\begin{parts}

%\part[4] $\displaystyle\lim_{x \to \infty} \sqrt{x^2+x} + x$

%\vfill

%\part[4] $\displaystyle\lim_{x \to -\infty} \sqrt{x^2+x} + x$

%\vfill

%\end{parts}


\newpage

\question[10] An open-top box is to be made by cutting small congruent squares from the
corners of a 12 inch by 12 inch sheet of tin and bending up the sides. How large should the
squares cut from the corners be to maximize the volume of the box?

\newpage




\question[10] Approximate the area under the graph of $y = x^3+ 10$ and above the $x$-axis
with $-2 \le x\le 2$ by using 4 rectangles (of equal width) with right end points. Remember that
you don't need to simplify your answer.

\newpage




\question[8] Does there exist a differentiable function $f$ such that $f(2) = 6,$ $f(5) = 8$ and
$f'(x) \ge 1$ for all $x$? Clearly justify your answer. If you use a theorem, state which theorem
you are using.


\newpage

%\newpage

%\question[10] Clearly mark the correct answer for each of the following by completely filling in
%the appropriate bubble. \textbf{No justification is needed.}

%\bigskip

%\begin{parts}
%\part If $f'(x) = 2$ everywhere and $f(2) = 4$, then $f(x) = 2x+2$.
% this is false because it fails f(2)=4
%\begin{itemize}[label={}]
%\item \chooseone True
%\item \chooseone False
%\end{itemize}

%\vspace{.4in}


%\end{parts}

\end{questions}

\end{document}
